---
title: "guilford voters"
output: html_notebook
---



```{r}
library(tidyverse)
lines <- read_csv("guilford06437.txt", col_names = FALSE) %>%
  rename(address = X1, town = X2, last_name = X3, first_name = X4, text_dob = X5, party = X6)
#View(lines)
```


```{r setup_for_call}
lines <- lines %>%
  mutate(addresses = paste0(address, ", ", town, ", CT"))
addresses <- data_frame(address = unique(lines$addresses))
addresses$id <- seq(1, nrow(addresses))
set1 <- 1:2000
set2 <- set1 + 2000
set3 <- set2 + 2400
set4 <- c(6401:8408, 4001:4400)
set5 <- c(8409:8608)
set4a <- set4[1:500]
set4b <- set4[501:1000]
set4c <- set4[1001:1500]
set4d <- set4[1501:2000]
set4e <- set4[2001:2408]

```



```{r basic_stats}
lines %>% group_by(party) %>% tally() %>% arrange(desc(n)) %>% 
  mutate(pct =paste0(round(100 * n / nrow(lines), 0),'%')) %>%
  bind_rows(lines  %>% tally() %>% mutate(party = "Total", pct = "")) %>%
kable(col.names = c("Party", "n", "%"), format = "html", format.args = list(big.mark = ","))

```

```{r find_households}
hh <- lines %>% group_by(address) %>% 
  tally()
```




Get a chunk of addresses
```{r get_addresses, message = TRUE}
addr_set1 <- geocode_addresses(addresses$address[set1])
addr_set1$id <- addresses$id[set1]
```
xx <- wrap_geocode("ksdfjsdfaf",23)
```{r set1, message = FALSE, include = FALSE}
library(purrr)
guilford_set1 <- map2_df(addresses$address[set1], addresses$id[set1], wrap_geocode, src = "google")
save(guilford_set1, file = "guilford_set1.RData")
```

```{r set2, include = FALSE}
if (geocodeQueryCheck() > nrow(addresses[set2,])) {
  guilford_set2 <- map2_df(addresses$address[set2], addresses$id[set2], wrap_geocode, src = "google")
  save(guilford_set2, file = "guilford_set2.RData")
  xx <- guilford_set2 %>% filter(rc != "OK")
  guilford_set2_missed <- map2_df(xx$in_address, xx$id, wrap_geocode)
  save(guilford_set2_missed, file = "guilford_set2_missed.RData")
}
```

```{r set3, message = FALSE, include = FALSE}
if (geocodeQueryCheck() > nrow(addresses[set3,])) {
  guilford_set3 <- map2_df(addresses$address[set3], addresses$id[set3], wrap_geocode, src = "google")
  save(guilford_set3, file = "guilford_set3.RData")
}
```

```{r set4a, message = FALSE, include = FALSE}
if (geocodeQueryCheck() > nrow(addresses[set4a,])) {
  guilford_set4a <- map2_df(addresses$address[set4a], addresses$id[set4a], wrap_geocode)
  save(guilford_set4a, file = "guilford_set4a.RData")
  table(guilford_set4a$rc, useNA = "ifany")
}
```

```{r set4e, message = FALSE, include = FALSE}
if (geocodeQueryCheck() > nrow(addresses[set4e,])) {
  guilford_set4e <- map2_df(addresses$address[set4e], addresses$id[set4e], wrap_geocode)
  save(guilford_set4e, file = "guilford_set4e.RData")
  table(guilford_set4e$rc, useNA = "ifany")
}
```

```{r set4c, message = FALSE, include = FALSE}
if (geocodeQueryCheck() > nrow(addresses[set4c,])) {
  set4ct <- setdiff(set4c, c(7642))
  guilford_set4c <- map2_df(addresses$address[set4ct], addresses$id[set4ct], wrap_geocode)
  save(guilford_set4c, file = "guilford_set4c.RData")
  table(guilford_set4c$rc, useNA = "ifany")
}
```



if (geocodeQueryCheck() > nrow(addresses[100:110,])) {
  xx <- map2_df(addresses$address[100:110], addresses$id[100:110], wrap_geocode, src = "google")

```{r bind_rows, include = FALSE}
guilford_addr <- bind_rows(guilford_set1, guilford_set2, guilford_set3, guilford_set4)
save(guilford_addr, file = "guilford_addr.RData")
guilford_addr <- guilford_addr %>% filter(lat > 40, lon < -70)
guilford_addr %>% filter(rc != "OK") %>% select(id,in_address)
```

Now let's merge the addresses back into line2

```{r}
lines3 <- lines2 %>% left_join(guilford_addr, by = c("addresses" = "in_address")) %>%
  mutate(party2 = case_when(
    party == "Independent" ~ "Ind or Unaffil",
    party == "U/i" ~ "Ind or Unaffil",
    party == "Unaffiliated" ~ "Ind or Unaffil",
    party == "Green" ~ "Ind or Unaffil",
    party == "Libertarian" ~ "Ind or Unaffil",
    TRUE ~ party
  ))
```

check for addresses outside of boundaries

```{r}
out_of_bounds <- guilford_addr %>% filter((lon < guilford_left_bottom_lon) | (lon > guilford_right_top_lon),
                                          (lat < guilford_left_bottom_lat) | (lat > guilford_right_top_lat))
```



```{r}
xx <- guilford_set1 %>% select(id, lat1 = lat, lon1 = lon, rc1 = rc) %>%
  left_join(guilford_addr %>% select(id, latdsk = lat, londsk = lon, rcdsk = rc, in_address))
yy <- xx %>% mutate(bad_lon = near(lon1, londsk), bad_lat = near(lat1, latdsk))
```

let's combimne all the google goetgge stuff

```{r}
load("guilford_set1.RData")
load("guilford_set2.RData")
load("guilford_set3.RData")
load("guilford_set4a.RData")
load("guilford_set4b.RData")
load("guilford_set4c.RData")
load("guilford_set4d.RData")
load("guilford_set4e.RData")

google_addr <- bind_rows(guilford_set1, guilford_set2, guilford_set3,
                         guilford_set4a, guilford_set4b, guilford_set4c, 
                         guilford_set4d, guilford_set4e)
missed <- addresses %>% filter(!(id %in% google_addr$id))

load("guilford_set5.RData")

google_addr <- bind_rows(google_addr, 
                         guilford_set5)
missed2 <- addresses %>% filter(!(id %in% google_addr$id))

google_addr <- bind_rows(google_addr, guilford_set6)
save(google_addr, file = "google_addr.RData")
```

```{r set5, message = FALSE, include = FALSE}
if (geocodeQueryCheck() > nrow(addresses[missed$id[251:544],])) {
  guilford_set5 <- map2_df(addresses$address[missed$id[251:544]], addresses$id[missed$id[251:544]], wrap_geocode)
  save(guilford_set5, file = "guilford_set5.RData")
  table(guilford_set5$rc, useNA = "ifany")
}
```

```{r set6, message = FALSE, include = FALSE}
library(ggmap)
missed2 <- missed2 %>% filter(address != "800 Village Walk Unit #175, Guilford, CT")
if (geocodeQueryCheck() > nrow(addresses[missed2$id,])) {
  guilford_set6 <- map2_df(addresses$address[missed2$id], addresses$id[missed2$id], wrap_geocode)
  save(guilford_set6, file = "guilford_set6.RData")
  table(guilford_set6$rc, useNA = "ifany")
}
```


Need to convert date to age
month_text <- c(" January ", " February ", " March ", " April ", 
  " May ", " June ", " July ", " August ", 
  " September", " October ", " November " " December ")
day_text <- c("-01-", "-02-", "-03-", "-04-", "-05-", "-06-", 
  "-07-", "-08-", "-09-", "-10-", "-11-", "-12-")
xx <- mutate(str_replace_all(text_dob, "born: ", "") %>%
  str_replace(" January ",  "-01-") %>%
  str_replace(" February ", "-02-") %>%
  str_replace(" March ",    "-03-") %>%
  str_replace(" April ",    "-04-") %>%
  str_replace(" May ",      "-05-") %>%
  str_replace(" June ",     "-06-") %>%
  str_replace(" July ",     "-07-") %>%
  str_replace(" August ",   "-08-") %>%
  str_replace(" September", "-09-") %>%
  str_replace(" October ",  "-10-") %>%
  str_replace(" November ", "-11-") %>%
  str_replace(" December ", "-12-") %>%
  dmy() %>%
  age(ymd("2017-11-03"))
lines$text_dob[which(is.na(xx))]

```{r}
# create named vector to use with str_replace that will find name and replace with value.
fnd <- c("born: ", " January ", " February ", " March ", " April ", 
                                 " May ", " June ", " July ", " August ", 
                                 " September ", " October ", " November ", " December ")
repl <- c("", "-01-", "-02-", "-03-", "-04-", 
                                 "-05-", "-06-", "-07-", "-08-", 
                                 "-09-", "-10-", "-11-", "-12-")
names(repl) <- fnd
xx <- lines %>% 
  mutate(age = compute_age(dmy(str_replace_all(text_dob, repl)), ymd("2017-11-03")),
         age = ifelse(age > 102, NA_real_, age))  
                               
```

